---
title: "Plots from Simulations (500 reps)"
format:
  html:
    embed-resources: true
editor: visual
---

```{r echo = FALSE, include=FALSE}
#| context: setup
library(knitr)
library(secr)
load("AllResults.RData")
AllResults40 <- Allresults[[1]]
AllResults120 <- Allresults[[2]]
```

``` {r echo = FALSE, include=FALSE}

```

# Relative bias plots

- Strata 1: D = 0.05 ; sigma = 200 m ; L0 = 2

- Strata 2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

## Grids with 800 m spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Grid40.800.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Grid40.800.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Grid40.800.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Grid120.800.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Grid120.800.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Grid120.800.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## Grids with 700 m spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Grid40.700.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Grid40.700.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Grid40.700.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Grid120.700.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Grid120.700.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Grid120.700.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## Clusters - OS spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Clust40.OS.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Clust40.OS.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Clust40.OS.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Clust120.OS.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Clust120.OS.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Clust120.OS.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## Clusters - 2 $\sigma$ spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Clust40.2sig.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Clust40.2sig.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$Clust40.2sig.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Clust120.2sig.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Clust120.2sig.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$Clust120.2sig.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA4 - S1 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA4 - S2 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA4 - Avg values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA4 - Both values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA4 - Both values (max-min)

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA5 - S1 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA5 - S2 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA5 - Avg values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA5 - Both values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## GA5 - Both values (max-min)

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

## Lacework

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$LW40.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$LW40.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.40$LW40.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$LW120.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(D1.ylim, D2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$LW120.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(L1.ylim, L2.ylim), se = F, rel.se = TRUE)
plot.results(simresults.120$LW120.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(Sig1.ylim, Sig2.ylim), se = F, rel.se = TRUE)
```
:::

# General comments - bias

## Grids
 - S1 and S2 D ests are skewed to the right for 800 m spacing but less so for 700 m
 - For 800 m spacing S1 sigma skewed to the left and S2 sigma to the right, for 700 m S1 more symmetrical and S2 skewed to the right
 - With 120 traps there are very few outliers for 700 m and 800 m spacing
 
## Clusters
 - OS spacings: some skewness for S2 D and Sigma
 - 2 * sigma spacing: slight positive skewness but balanced across the 2 strata
 - With 120 traps there are very few outliers for OS spacing. With 2 sigma spacing there is slight +ve skew in D for both and some +ve skew in S2 L0 and sigmas are symmetrical
 
## GA4

### S1 values
 - Some positive skewness in D (more for S2), slight for L0 and sigma (more for S1)
 - With 120 traps there are very few outliers
 
### S2 values
 - Slight positive skew in D and L0 for both strata, for sigma only for S2
 - With 120 traps slight +ve skew in D for S1 but others fairly symmetrical

### Avg values
 - Positive skewness in D and sigma, especially for S1
 - For S1, -ve bias in D and +ve bias in sigma
 - With 120 traps still substantial +ve skew in S1 D, other parameters fairly symmetrical
 
### Both values
 - Slight +ve skew across parameters (except for S1 sigma) but fairly balanced across strata
 - Max-min similar
 - With 120 traps dbns symmetrical with few outliers, for max-min there was slight +ve skew in the sigmas for both strata

## GA5

### S1 values
 - Some positive skewness in D (more for S2), slight for L0 and sigma fairly symmetrical
 - With 120 traps the dbns are mostly symmetrical with few outliers

### S2 values
 - Slight positive skew in D for S2, in L0 for S1, in sigma for both
 - With 120 traps very slight skew for S1 D otherwise symmetrical

### Avg values
 - Positive skewness in D, especially for S1
 - Slight skew across other parameters for both strata
 - For S1, -ve bias in D and +ve bias in sigma
 - Even with 120 traps substantial +ve skew in S1 D and slight bias in S1 sigma

### Both values
 - Very slight +ve skew in D for both, and sigma for S2
 - Max-min similar for D but L0 and sigma are more symmetrical
 - With 120 traps few outliers and mostly symmetrical dbns, same for max-min

## Lacework
 - Very slight skew but mostly more symmetrical dbns for all parameters
 - With 120 traps few outliers and mostly symmetrical dbns

# Relative SE plots

## Grids with 800 m spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Grid40.800.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Grid40.800.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Grid40.800.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Grid120.800.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Grid120.800.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Grid120.800.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## Grids with 700 m spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Grid40.700.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Grid40.700.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Grid40.700.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Grid120.700.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Grid120.700.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Grid120.700.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## Clusters - OS spacing

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Clust40.OS.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Clust40.OS.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Clust40.OS.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Clust120.OS.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Clust120.OS.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Clust120.OS.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## Clusters - 2 $\sigma$ spacing


::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$Clust40.2sig.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Clust40.2sig.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$Clust40.2sig.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$Clust120.2sig.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Clust120.2sig.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$Clust120.2sig.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA4 - S1 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA4 - S2 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA4 - Avg values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA4 - Both values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA4 - Both values (max min)

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA4.40.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA4.120.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::


## GA5 - S1 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.S1.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S1.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S1.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA5 - S2 values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.S2.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S2.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.S2.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA5 - Avg values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Avg.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA5 - Both values

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.Both.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Both.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.Both.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## GA5 - Both values (max-min)

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$GA5.40.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$GA5.120.BothMax.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

## Lacework

::: panel-tabset
### 40 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.40$LW40.D$Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$LW40.D$Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
plot.results(simresults.40$LW40.D$Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(se.lim,se.lim), se = TRUE, rel.se = TRUE)
```

### 120 Traps

```{r, echo = FALSE, fig.align="left"}
plot.results(simresults.120$LW120.D $Results, par = "D", true.value = c(0.05,0.05/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$LW120.D $Results, par = "L0", true.value = c(2, 2/15) , ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
plot.results(simresults.120$LW120.D $Results, par = "Sigma", true.value = c(200, 3000), ylim.ceiling = c(10,10), se = TRUE, rel.se = TRUE)
```
:::

# General comments - precision

## Grids
 - For 800 m spacing SE’s for all parameters skewed to the right (apart from S2 L0)
 - Improved for 700 m spacing, some skewness for S2 D and S2 sigma.
 - With 120 traps there are very few outliers, at 800 m spacing the most for S1 D and for 700 m spacing the most for S2 sigma

## Clusters
 - OS spacing: skewness for S2 D and sigma (as with bias)
 - 2 * sigma spacing: se’s quite tightly clustered for both strata and all parameters
 - With 120 traps there are very few outliers for both spacings

## GA4

### S1 values
 - More positive skewness in D for S2, and slightly more for S1 in sigma ses
 - With 120 traps there are very few outliers

### S2 values
 - Slight positive skewness in D for both strata, and more skew for S2 in sigma ses
 - With 120 traps some skew for S1 D is evident

### Avg values
 - Positive skewness across parameters, more so for S1
 - With 120 traps some skew for S1 D is evident with a few outliers for S1 sigma

### Both values
 - Some skew in S2 sigma but otherwise quite balanced
 - Max-min similar
 - With 120 traps tight dbns with few outliers, same for max-min

## GA5

### S1 values
 - More positive skewness in D for S2, and slightly more for S1 in sigma ses
 - With 120 traps there are very few outliers

### S2 values
 - Slight positive skew in D and sigma (mainly for S2)
 - With 120 traps very slight +ve skew in S1 D

### Avg values
 - Positive skewness in D, especially for S1
 - Slight skew in other parameters across both strata
 - Even with 120 traps substantial +ve skew in S1 D and some skew in S1 L0

### Both values
 - Very slight +ve skew in D for both, and sigma especially for S2
 - Max-min more skew for S2 D, and for sigma both are slightly skew
 - With 120 traps few outliers and mostly symmetrical dbns, with max-min a tiny bit more skewness in D and sigma for S1

## Lacework
 - Very slight skew in D and sigma for S2
 - With 120 traps few outliers and mostly symmetrical dbns