---
title: "Plots from Simulations (500 reps)"
format:
  html:
    embed-resources: true
editor: visual
---

```{r echo = FALSE, include=FALSE}
#| context: setup
library(knitr)
library(secr)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)

load("AllResults.RData")
AllResults40 <- Allresults[[1]]
AllResults120 <- Allresults[[2]]
AllResults40$traps  <- "40"
AllResults120$traps <- "120"

AllResults.combined <- bind_rows(AllResults40, AllResults120)
AllResults.combined$traps <- factor(AllResults.combined$traps, levels = c("40", "120"))

design_groups <- list(
  "Grids with 800 m spacing" = c("Grid 800m"),
  "Grids with 700 m spacing" = c("Grid 700m"),
  "Clusters - OS spacing" = c("Cluster (OS)"),
  "Clusters - 2 sigma spacing" = c("Cluster (2 Sig)"),
  "GA4 - S1 values" = c("GA4 S1"),
  "GA4 - S2 values" = c("GA4 S2"),
  "GA4 - Avg values" = c("GA4 Avg"),
  "GA4 - Both values" = c("GA4 Both"),
  "GA4 - Both values (max-min)" = c("GA4 Both (max-min)"),
  "GA5 - S1 values" = c("GA5 S1"),
  "GA5 - S2 values" = c("GA5 S2"),
  "GA5 - Avg values" = c("GA5 Avg"),
  "GA5 - Both values" = c("GA5 Both"),
  "GA5 - Both values (max-min)" = c("GA5 BothMax"),
  "Lacework" = c("Lacework")
)
params <- c("D", "L0", "Sig")
```

```{r echo = FALSE}
# define functions first
make.summary <- function(df) {
  df %>%
    
    # ✅ STEP 1: row-wise calculations
    mutate(
      lower = estimate - 1.96 * se,
      upper = estimate + 1.96 * se,
      covered = (lower <= truth) & (upper >= truth)
    ) %>%
    
    # ✅ STEP 2: summarise
    group_by(design, param, stratum) %>%
    summarise(
      n = n(),
      mean_est = mean(estimate, na.rm = TRUE),
      sd_est = sd(estimate, na.rm = TRUE),
      mean_se = mean(se, na.rm = TRUE),
      sd_se = sd(se, na.rm = TRUE),
      truth = first(truth),
      
      # ✅ coverage (now works)
      coverage = mean(covered, na.rm = TRUE),
      cov_se = sqrt(coverage * (1 - coverage) / n),
      
      # Precision
      RSE_emp = sd_est / truth,
      RSE_model = mean_se / truth,

      # ✅ NEW: SE of precision measures
      RSE_emp_se   = (sd_est / truth) / sqrt(2 * (n - 1)),
      RSE_model_se = (sd_se / sqrt(n)) / truth,
      
      # Bias
      RB = (mean_est - truth) / truth,
      RB_se = sd_est / (sqrt(n) * truth),
      
      .groups = "drop"
    ) %>%
    
    # ✅ STEP 3: formatting / labels (unchanged)
    mutate(
      design_group = case_when(
        grepl("Grid", design) ~ "Grid",
        grepl("Cluster", design) | grepl("Lacework", design) ~ "Cluster",
        grepl("GA4", design) ~ "Optimised 1",
        grepl("GA5", design) ~ "Optimised 2",
        TRUE ~ "Other"
      ),
      
      design_group = factor(
        design_group,
        levels = c("Grid", "Cluster", "Optimised 1", "Optimised 2")
      ),
      
      param = case_when(
        param == "D"  ~ "Density",
        param == "L0" ~ "lambda[0]",
        param == "Sig" ~ "sigma"
      ),
      
      design = factor(
        design,
        levels = c(
          "Grid 700m", "Grid 800m",
          "Cluster (OS)", "Cluster (2 Sig)",
          "Lacework",
          "GA4 S1", "GA4 S2", "GA4 Avg", "GA4 Both", "GA4 Both (max-min)",
          "GA5 S1", "GA5 S2", "GA5 Avg", "GA5 Both", "GA5 BothMax"
        ),
        labels = c(
          "Gr.700", "Gr.800",
          "Cl(OS)", "Cl(2 Sig)",
          "LW",
          "GA4 S1", "GA4 S2", "GA4 Avg", "GA4 Both", "GA4 Both (max-min)",
          "GA5 S1", "GA5 S2", "GA5 Avg", "GA5 Both", "GA5 BothMax"
        )
      )
    )
}

#general plotting function to use for RB and coverage (and maybe others)
#yvar - column name as string (e.g. "RB")
#sevar: SE column (e.g. "RB_se")
#ylab: y-axis label
#yline: reference line (e.g. 0 or 0.95)
plot_metric <- function(sum.df, yvar, sevar, ylab, yline = NULL, plot.title, ylims = NULL) {
  
  ggplot(sum.df,
         aes(x = design,
             y = .data[[yvar]],
             colour = design_group,
             shape = traps,
             group = interaction(design_group, traps))) +
    
    # ✅ shading
    geom_rect(
      data = data.frame(
        xmin = c(0.5, 2.5, 5.5, 10.5),
        xmax = c(2.5, 5.5, 10.5, 15.5),
        ymin = -Inf,
        ymax = Inf,
        fill_col = c("#1b9e77", "#d95f02", "#6a51a3", "#bcbddc")
      ),
      aes(xmin = xmin, xmax = xmax,
          ymin = ymin, ymax = ymax,
          fill = fill_col),
      inherit.aes = FALSE,
      alpha = 0.08
    ) +
    scale_fill_identity() +
    
    # ✅ points
    geom_point(
      size = 2,
      position = position_dodge(width = 0.5)
    ) +
    
    # ✅ error bars
    geom_errorbar(
      aes(ymin = .data[[yvar]] - 2 * .data[[sevar]],
          ymax = .data[[yvar]] + 2 * .data[[sevar]]),
      width = 0.2,
      position = position_dodge(width = 0.5)
    ) +
    
    # ✅ optional reference line
    {if (!is.null(yline))
      geom_hline(yintercept = yline,
                 linetype = "dashed",
                 colour = "black",
                 linewidth = 0.8)
    } +
    
    # ✅ facets
    facet_grid(
      param ~ stratum,
      labeller = labeller(
        param = label_parsed,
        stratum = c("S1" = "Stratum 1",
                    "S2" = "Stratum 2")
      )
    ) +
    
    # ✅ colours
    scale_colour_manual(
      name = "Design type",
      values = c(
        "Grid" = "#1b9e77",
        "Cluster" = "#d95f02",
        "Optimised 1" = "#6a51a3",
        "Optimised 2" = "#7570b3"
      )
    ) +
    
    # ✅ shapes (traps)
    scale_shape_manual(
      name = "Traps",
      values = c("40" = 16, "120" = 17),
      labels = c("40" = "40 traps", "120" = "120 traps")
    ) +
    
    # ✅ limits
    {if (!is.null(ylims)) coord_cartesian(ylim = ylims)} +
    
    # ✅ theme
    theme_bw() +
    theme(
      axis.text.x = element_text(size = 10, angle = 60, hjust = 1),
      strip.text = element_text(size = 12),
      legend.position = "top",
      panel.spacing = unit(0.5, "lines"),
      plot.margin = margin(5, 5, 5, 5)
    ) +
    
    # ✅ labels
    labs(
      y = ylab,
      x = "Design",
      title = plot.title
    )
}

#plotting two measures of precision, incl error bars
Prec.plot <- function(sum.df, plot.title, ylims){
  
  #reshape so that the two Rel SEs can be compared
  precision_long <- sum.df %>%
    mutate(
      type_emp   = "Empirical",
      type_model = "Model-based"
    ) %>%
    pivot_longer(
      cols = c(RSE_emp, RSE_model),
      names_to = "type",
      values_to = "RSE"
    ) %>%
    mutate(
      type = recode(type,
                    RSE_emp = "Empirical",
                    RSE_model = "Model-based"),
      RSE_se = case_when(
        type == "Empirical"   ~ RSE_emp_se,
        type == "Model-based" ~ RSE_model_se
      )
    )

  ggplot(precision_long,
         aes(x = design,
             y = RSE,
             colour = design_group,
             shape = type,
             group = interaction(type, traps))) +
    
    # ✅ shading
    geom_rect(
      data = data.frame(
        xmin = c(0.5, 2.5, 5.5, 10.5),
        xmax = c(2.5, 5.5, 10.5, 15.5),
        ymin = -Inf,
        ymax = Inf,
        fill_col = c("#1b9e77", "#d95f02", "#6a51a3", "#bcbddc")
      ),
      aes(xmin = xmin, xmax = xmax,
          ymin = ymin, ymax = ymax,
          fill = fill_col),
      inherit.aes = FALSE,
      alpha = 0.08
    ) +
    scale_fill_identity() +
    
    # ✅ points
    geom_point(
      size = 2,
      position = position_dodge(width = 0.4)
    ) +
    
    # ✅ NEW: error bars (mean ± 2 SE)
    geom_errorbar(
      aes(
        ymin = RSE - 2 * RSE_se,
        ymax = RSE + 2 * RSE_se
      ),
      width = 0.2,
      position = position_dodge(width = 0.4)
    ) +
    
    # ✅ facets
    facet_grid(
      param ~ stratum,
      labeller = labeller(
        param = label_parsed,
        stratum = c("S1" = "Stratum 1",
                    "S2" = "Stratum 2")
      )
    ) +
    
    # ✅ colours
    scale_colour_manual(
      name = "Design type",
      values = c(
        "Grid" = "#1b9e77",
        "Cluster" = "#d95f02",
        "Optimised 1" = "#6a51a3",
        "Optimised 2" = "#bcbddc"
      )
    ) +
    
    # ✅ shapes
    scale_shape_manual(
      name = "Precision type",
      values = c(
        "Empirical" = 16,
        "Model-based" = 17
      )
    ) +
    
    coord_cartesian(ylim = ylims) +
    
    theme_bw() +
    theme(
      axis.text.x = element_text(size = 10, angle = 60, hjust = 1),
      strip.text = element_text(size = 12),
      legend.position = "top"
    ) +
    
    labs(
      y = "Relative Standard Error",
      x = "Design",
      title = plot.title
    )

}

#operates on combined df
plot_param_combined <- function(df, design_name, param_name,
                               use_se = FALSE, rel_se = TRUE) {
  
  param_labels <- c(
    D = "Density",
    L0 = "lambda[0]",
    Sig = "sigma"
  )
  
  param_expr <- function(p) {
    parse(text = param_labels[[p]])[[1]]
  }
  
  sub <- df %>%
    filter(
      design == design_name,
      param == param_name
    )
  
  # ✅ SAFE logic
  if (!use_se) {
    sub <- sub %>% mutate(y = estimate)
  } else if (rel_se) {
    sub <- sub %>% mutate(y = se / truth)
  } else {
    sub <- sub %>% mutate(y = se)
  }
  
  sub <- sub %>% filter(is.finite(y))
  
  ggplot(sub, aes(x = traps, y = y, fill = traps)) +
    
    geom_boxplot(width = 0.6, outlier.size = 0.6, alpha = 0.7) +
    
    facet_wrap(~ stratum, scales = "free_y") +
    
    # ✅ FIXED HERE
    {if (!use_se)
      geom_hline(aes(yintercept = truth),
                 linetype = "dashed",
                 linewidth = 0.6,
                 colour = "black")
    } +
    
    theme_bw(base_size = 13) +
    theme(
      legend.position = "none",
      axis.title.y = element_text(size = 16)
    ) +
    
    labs(
      title = design_name,
      y = if (!use_se) {
        bquote("Estimates of " ~ .(param_expr(param_name)))
      } else if (rel_se) {
        bquote("Relative SE of " ~ .(param_expr(param_name)))
      } else {
        bquote("SE of " ~ .(param_expr(param_name)))
      },
      x = "Number of traps"
    )
}

#new fn to tab the parameters
plot_block_tabs <- function(df, design_name,
                            use_se = FALSE, rel_se = TRUE) {

  cat("::: panel-tabset\n\n")

  
  nice_names <- c(
      D   = "Density",
      L0  = "λ₀",
      Sig = "σ"
    )

  for (p in params) {

    # ✅ Use the nice label instead of raw "D", "L0", "Sig"
    cat("###", nice_names[[p]], "\n\n")

    print(
      plot_param_combined(
        df,
        design_name = design_name,
        param_name = p,
        use_se = use_se,
        rel_se = rel_se
      )
    )

    cat("\n\n")  # reset markdown (important for tab parsing)
  }

  cat(":::\n\n")
}
```

# Simulation setup

- Strata 1: D = 0.05 ; sigma = 200 m ; L0 = 2

- Strata 2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

```{r echo = FALSE}
#create summaries
summary.40 <- make.summary(AllResults40)
summary.120 <- make.summary(AllResults120)
summary.40$traps  <- "40"
summary.120$traps <- "120"
summary.combined <- dplyr::bind_rows(summary.40, summary.120)
summary.combined$traps <- factor(summary.combined$traps, levels = c("40", "120"))
```

# Relative bias plots

```{r echo = FALSE,  fig.height=12}
#RB plot, both trap lvls
plot_metric(summary.combined,
            yvar = "RB",
            sevar = "RB_se",
            ylab = "Relative Bias",
            yline = 0,
            plot.title = "Relative Bias",
            ylims = c(-0.2, 1))
```

## General comments - bias

### Grids

- S1 and S2 D ests are skewed to the right for 800 m spacing but less so for 700 m
- For 800 m spacing S1 sigma skewed to the left and S2 sigma to the right, for 700 m S1 more symmetrical and S2 skewed to the right
- With 120 traps there are very few outliers for 700 m and 800 m spacing

### Clusters

- OS spacings: some skewness for S2 D and Sigma
- 2 \* sigma spacing: slight positive skewness but balanced across the 2 strata
- With 120 traps there are very few outliers for OS spacing. With 2 sigma spacing there is slight +ve skew in D for both and some +ve skew in S2 L0 and sigmas are symmetrical

### GA4

#### S1 values

- Some positive skewness in D (more for S2), slight for L0 and sigma (more for S1)
- With 120 traps there are very few outliers

#### S2 values

- Slight positive skew in D and L0 for both strata, for sigma only for S2
- With 120 traps slight +ve skew in D for S1 but others fairly symmetrical

#### Avg values

- Positive skewness in D and sigma, especially for S1
- For S1, -ve bias in D and +ve bias in sigma
- With 120 traps still substantial +ve skew in S1 D, other parameters fairly symmetrical

#### Both values

- Slight +ve skew across parameters (except for S1 sigma) but fairly balanced across strata
- Max-min similar
- With 120 traps dbns symmetrical with few outliers, for max-min there was slight +ve skew in the sigmas for both strata

### GA5

#### S1 values

- Some positive skewness in D (more for S2), slight for L0 and sigma fairly symmetrical
- With 120 traps the dbns are mostly symmetrical with few outliers

#### S2 values

- Slight positive skew in D for S2, in L0 for S1, in sigma for both
- With 120 traps very slight skew for S1 D otherwise symmetrical

#### Avg values

- Positive skewness in D, especially for S1
- Slight skew across other parameters for both strata
- For S1, -ve bias in D and +ve bias in sigma
- Even with 120 traps substantial +ve skew in S1 D and slight bias in S1 sigma

#### Both values

- Very slight +ve skew in D for both, and sigma for S2
- Max-min similar for D but L0 and sigma are more symmetrical
- With 120 traps few outliers and mostly symmetrical dbns, same for max-min

### Lacework

- Very slight skew but mostly more symmetrical dbns for all parameters
- With 120 traps few outliers and mostly symmetrical dbns

# Excluded reps

```{r echo = FALSE}
df_excl <- AllResults.combined %>%   # or your combined df
  mutate(traps = factor(traps, levels = c("40", "120"))) %>%
  group_by(sim, design, stratum, traps) %>%
  summarise(
    bad_sim = any(is.na(estimate)),
    .groups = "drop"
  ) %>%
  group_by(design, stratum, traps) %>%
  summarise(
    n_bad   = sum(bad_sim),
    n_sims  = n(),
    prop_bad = n_bad / n_sims,
    .groups = "drop"
  )
```

```{r echo = FALSE,  fig.height=5}
ggplot(df_excl,
       aes(x = design,
           y = prop_bad,
           fill = stratum)) +
  
  # ✅ bars (side-by-side within each design)
  geom_col(
    position = position_dodge(width = 0.75),
    width = 0.7
  ) +
  
    # ✅ separate panels for 40 vs 120 traps
  facet_wrap(~ traps) +
  
  # ✅ nice colours for strata
  scale_fill_manual(
    name = "Stratum",
    values = c(
      "S1" = "#1b9e77",
      "S2" = "#d95f02"
    ),
    labels = c(
      "S1" = "Stratum 1",
      "S2" = "Stratum 2"
    )
  ) +
  
  # ✅ show % on axis
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  
  # ✅ theme
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1),
    legend.position = "top",
    strip.text = element_text(size = 12)
  ) +
  
  # ✅ labels
  labs(
    y = "Proportion excluded",
    x = "Design",
    title = "Simulation exclusion %"
  )
```

# Relative SE plots

```{r echo = FALSE,  fig.height=12}
#Precision plot, 40 traps
Prec.plot(summary.40, "Relative SE (40 traps)", ylims = c(0, 1.75))

#Precision plot, 120 traps
Prec.plot(summary.120, "Relative SE (120 traps)", ylims = c(0, 1.75))

#plot of empirical SE for both trap lvls
plot_metric(summary.combined,
            yvar = "RSE_emp",
            sevar = "RSE_emp_se",
            ylab = "Relative SE (empirical)",
            yline = NULL,
            plot.title = "Relative SE (empirical)",
            ylims = c(0, 1.5))
```

# Coverage plots

```{r echo = FALSE,  fig.height=12}
#Coverage for both trap lvls
plot_metric(summary.combined,
            yvar = "coverage",
            sevar = "cov_se",
            ylab = "Coverage probability",
            yline = 0.95,
            plot.title = "Coverage",
            ylims = c(0.7, 1.0))
```

# Boxplots of estimates

```{r echo=FALSE, results='asis', warning=FALSE,  fig.height = 6}
walk(names(design_groups), function(group_name) {

  cat("##", group_name, "\n\n")

  for (d in design_groups[[group_name]]) {
    plot_block_tabs(AllResults.combined, d, use_se = FALSE)
  }
})
```

# Boxplots of standard errors

```{r echo=FALSE, results='asis', warning=FALSE,  fig.height = 6}
walk(names(design_groups), function(group_name) {

  cat("##", group_name, "\n\n")

  for (d in design_groups[[group_name]]) {
    plot_block_tabs(AllResults.combined, d, use_se = TRUE)
  }
})
```

## General comments - precision

### Grids

- For 800 m spacing SE’s for all parameters skewed to the right (apart from S2 L0)
- Improved for 700 m spacing, some skewness for S2 D and S2 sigma.
- With 120 traps there are very few outliers, at 800 m spacing the most for S1 D and for 700 m spacing the most for S2 sigma

### Clusters

- OS spacing: skewness for S2 D and sigma (as with bias)
- 2 \* sigma spacing: se’s quite tightly clustered for both strata and all parameters
- With 120 traps there are very few outliers for both spacings

### GA4

#### S1 values

- More positive skewness in D for S2, and slightly more for S1 in sigma ses
- With 120 traps there are very few outliers

#### S2 values

- Slight positive skewness in D for both strata, and more skew for S2 in sigma ses
- With 120 traps some skew for S1 D is evident

#### Avg values

- Positive skewness across parameters, more so for S1
- With 120 traps some skew for S1 D is evident with a few outliers for S1 sigma

#### Both values

- Some skew in S2 sigma but otherwise quite balanced
- Max-min similar
- With 120 traps tight dbns with few outliers, same for max-min

### GA5

#### S1 values

- More positive skewness in D for S2, and slightly more for S1 in sigma ses
- With 120 traps there are very few outliers

#### S2 values

- Slight positive skew in D and sigma (mainly for S2)
- With 120 traps very slight +ve skew in S1 D

#### Avg values

- Positive skewness in D, especially for S1
- Slight skew in other parameters across both strata
- Even with 120 traps substantial +ve skew in S1 D and some skew in S1 L0

#### Both values

- Very slight +ve skew in D for both, and sigma especially for S2
- Max-min more skew for S2 D, and for sigma both are slightly skew
- With 120 traps few outliers and mostly symmetrical dbns, with max-min a tiny bit more skewness in D and sigma for S1

### Lacework

- Very slight skew in D and sigma for S2
- With 120 traps few outliers and mostly symmetrical dbns
