---
title: "Plots from Simulations (500 reps)"
format:
  html:
    embed-resources: true
editor: visual
---

```{r echo = FALSE, include=FALSE}
#| context: setup
library(knitr)
library(secr)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)

load("AllResults.RData")
AllResults40 <- Allresults[[1]]
AllResults120 <- Allresults[[2]]

design_groups <- list(
  "Grids with 800 m spacing" = c("Grid 800m"),
  "Grids with 700 m spacing" = c("Grid 700m"),
  "Clusters - OS spacing" = c("Cluster (OS)"),
  "Clusters - 2 sigma spacing" = c("Cluster (2 Sig)"),
  "GA4 - S1 values" = c("GA4 S1"),
  "GA4 - S2 values" = c("GA4 S2"),
  "GA4 - Avg values" = c("GA4 Avg"),
  "GA4 - Both values" = c("GA4 Both"),
  "GA4 - Both values (max-min)" = c("GA4 Both (max-min)"),
  "GA5 - S1 values" = c("GA5 S1"),
  "GA5 - S2 values" = c("GA5 S2"),
  "GA5 - Avg values" = c("GA5 Avg"),
  "GA5 - Both values" = c("GA5 Both"),
  "GA5 - Both values (max-min)" = c("GA5 BothMax"),
  "Lacework" = c("Lacework")
)
params <- c("D", "L0", "Sig")
```


```{r echo = FALSE}
# define functions first
plot_param_raw <- function(df, design_name, param_name, se = FALSE, rel_se = TRUE, ylim = NULL) {
  
  param_labels <- c(
    D = "Density",
    L0 = "lambda[0]",
    Sig = "sigma"
  )

  param_expr <- function(p) {
    parse(text = param_labels[[p]])[[1]]
  }
  
  sub <- df %>%
    filter(
      design == design_name,
      param == param_name
    )
  
  # choose variable
  if (!se) {
    sub <- sub %>% mutate(y = estimate)
  } else {
    if (rel_se) {
      sub <- sub %>% mutate(y = se / truth)
    } else {
      sub <- sub %>% mutate(y = se)
    }
  }
  
  ggplot(sub, aes(x = 1, y = y)) +
    
    geom_boxplot(outlier.alpha = 0.3) +
    
    # ✅ separate panels per stratum with independent scales
    facet_wrap(~ stratum, scales = "free_y") +
    
    # ✅ truth line per panel (only for estimates)
    {if (!se) geom_hline(aes(yintercept = truth),
                         linetype = "dashed",
                         colour = "red")} +
    
    theme_bw() +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
    ) +

    labs(
      title = design_name,  # keep title simple
      
      y = if (!se) {
        bquote("Estimates of" ~ .(param_expr(param_name)))
      } else if (rel_se) {
        bquote("Relative SE of" ~ .(param_expr(param_name)))
      } else {
        bquote("SE of" ~ .(param_expr(param_name)))
      },
      x = NULL
    )
}

plot_block <- function(df, design_name, se = FALSE, rel_se = TRUE) {
  
  plots <- lapply(params, function(p) {
    plot_param_raw(
      df,
      design_name = design_name,
      param_name = p,
      se = se,
      rel_se = rel_se
    )
  })
  
  # ✅ Important: print plots so Quarto renders them
  for (p in plots) suppressWarnings(print(p))
}
```

```{r echo = FALSE}
#function to calc appropriate summaries
make.summary <- function(df) {
  df %>%
    
    # ✅ STEP 1: row-wise calculations
    mutate(
      lower = estimate - 1.96 * se,
      upper = estimate + 1.96 * se,
      covered = (lower <= truth) & (upper >= truth)
    ) %>%
    
    # ✅ STEP 2: summarise
    group_by(design, param, stratum) %>%
    summarise(
      n = n(),
      mean_est = mean(estimate, na.rm = TRUE),
      sd_est = sd(estimate, na.rm = TRUE),
      mean_se = mean(se, na.rm = TRUE),
      truth = first(truth),
      
      # ✅ coverage (now works)
      coverage = mean(covered, na.rm = TRUE),
      cov_se = sqrt(coverage * (1 - coverage) / n),
      
      # Precision
      RSE_emp = sd_est / truth,
      RSE_model = mean_se / truth,
      
      # Bias
      RB = (mean_est - truth) / truth,
      RB_se = sd_est / (sqrt(n) * truth),
      
      .groups = "drop"
    ) %>%
    
    # ✅ STEP 3: formatting / labels (unchanged)
    mutate(
      design_group = case_when(
        grepl("Grid", design) ~ "Grid",
        grepl("Cluster", design) | grepl("Lacework", design) ~ "Cluster",
        grepl("GA4", design) ~ "Optimised 1",
        grepl("GA5", design) ~ "Optimised 2",
        TRUE ~ "Other"
      ),
      
      design_group = factor(
        design_group,
        levels = c("Grid", "Cluster", "Optimised 1", "Optimised 2")
      ),
      
      param = case_when(
        param == "D"  ~ "Density",
        param == "L0" ~ "lambda[0]",
        param == "Sig" ~ "sigma"
      ),
      
      design = factor(
        design,
        levels = c(
          "Grid 700m", "Grid 800m",
          "Cluster (OS)", "Cluster (2 Sig)",
          "Lacework",
          "GA4 S1", "GA4 S2", "GA4 Avg", "GA4 Both", "GA4 Both (max-min)",
          "GA5 S1", "GA5 S2", "GA5 Avg", "GA5 Both", "GA5 BothMax"
        ),
        labels = c(
          "Gr.700", "Gr.800",
          "Cl(OS)", "Cl(2 Sig)",
          "LW",
          "GA4 S1", "GA4 S2", "GA4 Avg", "GA4 Both", "GA4 Both (max-min)",
          "GA5 S1", "GA5 S2", "GA5 Avg", "GA5 Both", "GA5 BothMax"
        )
      )
    )
}

#plotting functions
RB.plot <- function(sum.df, plot.title, ylims){
  ggplot(sum.df, aes(x = design, y = RB, colour = design_group)) +
    
    # ✅ Shading (4 groups, with similar colours for 3a and 3b)
    
    geom_rect(
      data = data.frame(
        xmin = c(0.5, 2.5, 5.5, 10.5),
        xmax = c(2.5, 5.5, 10.5, 15.5),
        ymin = -Inf,
        ymax = Inf,
        fill_col = c("#1b9e77", "#d95f02", "#6a51a3", "#bcbddc")
      ),
      aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill_col),
      inherit.aes = FALSE,
      alpha = 0.08
    ) +
    scale_fill_identity() +
    
    
    # ✅ Data
    geom_point(size = 2) +
    geom_errorbar(
      aes(ymin = RB - 2 * RB_se, ymax = RB + 2 * RB_se),
      width = 0.2
    ) +
    
    # ✅ Facets
    facet_grid(
      param ~ stratum,
      labeller = labeller(
        param = label_parsed,
        stratum = c(
          "S1" = "Stratum 1",
          "S2" = "Stratum 2"
        )
      )
    ) +
    
    # ✅ Reference line
    geom_hline(yintercept = 0, linetype = "dashed") +
    
    # ✅ Point colours (group-based)
    scale_colour_manual(
      name = "Design type",
      values = c(
        "Grid" = "#1b9e77",
        "Cluster" = "#d95f02",
        "Optimised 1" = "#6a51a3",
        "Optimised 2" = "#7570b3"
      )
    ) +
    coord_cartesian(ylim = ylims) +
    
    # ✅ Theme
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 60, hjust = 1),
      legend.position = "top",
      strip.text = element_text(size = 11),   # increase from default (~10),
      panel.spacing = unit(0.5, "lines"),
      plot.margin = margin(5, 5, 5, 5)
    ) +
    
    labs(
      y = "Relative Bias",
      x = "Design",
      title = plot.title
    )
}

Prec.plot <- function(sum.df, plot.title, ylims){
  
  #reshape so that the two Rel SEs can be compared
  precision_long <- sum.df %>%
    pivot_longer(
      cols = c(RSE_emp, RSE_model),
      names_to = "type",
      values_to = "RSE"
    )
  
  precision_long$type <- recode(precision_long$type,
                                RSE_emp = "Empirical",
                                RSE_model = "Model-based"
  )
  
  ggplot(precision_long,
         aes(x = design, y = RSE, colour = design_group, shape = type)) +
    
    # ✅ Same shading as before
    geom_rect(
      data = data.frame(
        xmin = c(0.5, 2.5, 5.5, 10.5),
        xmax = c(2.5, 5.5, 10.5, 15.5),
        ymin = -Inf,
        ymax = Inf,
        fill_col = c("#1b9e77", "#d95f02", "#6a51a3", "#bcbddc")
      ),
      aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill_col),
      inherit.aes = FALSE,
      alpha = 0.08
    ) +
    scale_fill_identity() +
    
    # ✅ Points (now two per design)
    geom_point(size = 2, position = position_dodge(width = 0.4)) +
    
    # ✅ Facets
    facet_grid(
      param ~ stratum,
      labeller = labeller(
        param = label_parsed,
        stratum = c("S1" = "Stratum 1", "S2" = "Stratum 2")
      )
    ) +
    
    # ✅ Colour scale
    scale_colour_manual(
      name = "Design type",
      values = c(
        "Grid" = "#1b9e77",
        "Cluster" = "#d95f02",
        "Optimised 1" = "#6a51a3",
        "Optimised 2" = "#bcbddc"
      )
    ) +
    
    # ✅ Shape scale for precision type
    scale_shape_manual(
      name = "Precision type",
      values = c(
        "Empirical" = 16,   # filled circle
        "Model-based" = 17  # triangle
      )
    ) +
    coord_cartesian(ylim = ylims) +
    theme_bw() +
    theme(
      axis.text.x = element_text(size = 10, angle = 60, hjust = 1),
      strip.text = element_text(size = 11),
      legend.position = "top",
      panel.spacing = unit(0.5, "lines"),
      plot.margin = margin(5, 5, 5, 5)
    ) +
    
    labs(
      y = "Relative Standard Error",
      x = "Design",
      title = plot.title
    )
}

Coverage.plot <- function(sum.df, plot.title, ylims){
  ggplot(sum.df, aes(x = design, y = coverage, colour = design_group)) +
    
    # ✅ same shading
    geom_rect(
      data = data.frame(
        xmin = c(0.5, 2.5, 5.5, 10.5),
        xmax = c(2.5, 5.5, 10.5, 15.5),
        ymin = -Inf,
        ymax = Inf,
        fill_col = c("#1b9e77", "#d95f02", "#6a51a3", "#bcbddc")
      ),
      aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill_col),
      inherit.aes = FALSE,
      alpha = 0.08
    ) +
    scale_fill_identity() +
    
    # ✅ points
    geom_point(size = 2) +
    
    # ✅ optional error bars
    geom_errorbar(
      aes(ymin = coverage - 2 * cov_se, ymax = coverage + 2 * cov_se),
      width = 0.2
    ) +
    
    # ✅ target line
    geom_hline(yintercept = 0.95, linetype = "dashed", colour = "black", linewidth = 0.8) +
    
    # ✅ facets
    facet_grid(
      param ~ stratum,
      labeller = labeller(
        param = label_parsed,
        stratum = c("S1" = "Stratum 1", "S2" = "Stratum 2")
      )
    ) +
    
    # ✅ colours
    scale_colour_manual(
      name = "Design type",
      values = c(
        "Grid" = "#1b9e77",
        "Cluster" = "#d95f02",
        "Optimised 1" = "#6a51a3",
        "Optimised 2" = "#bcbddc"
      )
    ) +
    
    coord_cartesian(ylim = ylims) +
    
    theme_bw() +
    theme(
      axis.text.x = element_text(size = 10, angle = 60, hjust = 1),
      strip.text = element_text(size = 11),
      legend.position = "top",
      panel.spacing = unit(0.5, "lines"),
      plot.margin = margin(5, 5, 5, 5)
    ) +
    
    labs(
      y = "Coverage probability",
      x = "Design",
      title = plot.title
    )
}
```

# Simulation setup

- Strata 1: D = 0.05 ; sigma = 200 m ; L0 = 2

- Strata 2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

```{r echo = FALSE}
#create summaries
summary.40 <- make.summary(AllResults40)
summary.120 <- make.summary(AllResults120)
summary.40$traps  <- "40"
summary.120$traps <- "120"
summary.combined <- dplyr::bind_rows(summary.40, summary.120)
```

# Relative bias plots

```{r echo = FALSE,  fig.width=11, fig.height=9}
#RB plot, 40 traps
RB.plot(summary.40, "Relative Bias (40 traps)", ylims = c(0, 0.5))

#RB plot, 120 traps
RB.plot(summary.120, "Relative Bias (120 traps)", ylims = c(0, 0.5))
```

```{r echo = FALSE,  fig.width=11, fig.height=9}
#multi-panel for 40 / 120
RB.plot2(summary.combined, "Relative Bias", ylims = c(0, 0.5))
```


```{r echo = FALSE,  fig.width=11, fig.height=9}
#RB plot, 40 traps
RB.plot.combined(summary.combined, "Both trap levels on the same plot", ylims = c(0, 0.5))
```

# Relative SE plots

```{r echo = FALSE,  fig.width=11, fig.height=9}
#Precision plot, 40 traps
Prec.plot(summary.40, "Relative SE (40 traps)", ylims = c(0, 1.5))

#Precision plot, 120 traps
Prec.plot(summary.120, "Relative SE (120 traps)", ylims = c(0, 1.5))
```

# Coverage plots

```{r echo = FALSE,  fig.width=11, fig.height=9}
#Coverage, 40 traps
Coverage.plot(summary.40, "Coverage of 95% Confidence Intervals (40 traps)", ylims = c(0.8,1))

#Coverage, 120 traps
Coverage.plot(summary.120, "Coverage of 95% Confidence Intervals (120 traps)", ylims = c(0.8,1))
```

# Boxplots of estimates 

```{r echo=FALSE, results='asis', warning=FALSE,  fig.width = 6, fig.height = 9}
walk(names(design_groups), function(group_name) {

  cat("##", group_name, "\n\n")
  cat("::: panel-tabset\n\n")

  # ✅ 40 traps
  cat("### 40 Traps\n\n")
  for (d in design_groups[[group_name]]) {
    plot_block(AllResults40, d, se = FALSE)
  }

  # ✅ CRITICAL: TWO newlines BEFORE header
  cat("\n\n### 120 Traps\n\n")

  for (d in design_groups[[group_name]]) {
    plot_block(AllResults120, d, se = FALSE)
  }

  # ✅ closing block
  cat("\n:::\n\n")
})
```

# General comments - bias

## Grids
 - S1 and S2 D ests are skewed to the right for 800 m spacing but less so for 700 m
 - For 800 m spacing S1 sigma skewed to the left and S2 sigma to the right, for 700 m S1 more symmetrical and S2 skewed to the right
 - With 120 traps there are very few outliers for 700 m and 800 m spacing
 
## Clusters
 - OS spacings: some skewness for S2 D and Sigma
 - 2 * sigma spacing: slight positive skewness but balanced across the 2 strata
 - With 120 traps there are very few outliers for OS spacing. With 2 sigma spacing there is slight +ve skew in D for both and some +ve skew in S2 L0 and sigmas are symmetrical
 
## GA4

### S1 values
 - Some positive skewness in D (more for S2), slight for L0 and sigma (more for S1)
 - With 120 traps there are very few outliers
 
### S2 values
 - Slight positive skew in D and L0 for both strata, for sigma only for S2
 - With 120 traps slight +ve skew in D for S1 but others fairly symmetrical

### Avg values
 - Positive skewness in D and sigma, especially for S1
 - For S1, -ve bias in D and +ve bias in sigma
 - With 120 traps still substantial +ve skew in S1 D, other parameters fairly symmetrical
 
### Both values
 - Slight +ve skew across parameters (except for S1 sigma) but fairly balanced across strata
 - Max-min similar
 - With 120 traps dbns symmetrical with few outliers, for max-min there was slight +ve skew in the sigmas for both strata

## GA5

### S1 values
 - Some positive skewness in D (more for S2), slight for L0 and sigma fairly symmetrical
 - With 120 traps the dbns are mostly symmetrical with few outliers

### S2 values
 - Slight positive skew in D for S2, in L0 for S1, in sigma for both
 - With 120 traps very slight skew for S1 D otherwise symmetrical

### Avg values
 - Positive skewness in D, especially for S1
 - Slight skew across other parameters for both strata
 - For S1, -ve bias in D and +ve bias in sigma
 - Even with 120 traps substantial +ve skew in S1 D and slight bias in S1 sigma

### Both values
 - Very slight +ve skew in D for both, and sigma for S2
 - Max-min similar for D but L0 and sigma are more symmetrical
 - With 120 traps few outliers and mostly symmetrical dbns, same for max-min

## Lacework
 - Very slight skew but mostly more symmetrical dbns for all parameters
 - With 120 traps few outliers and mostly symmetrical dbns

# Boxplots of standard errors

```{r echo=FALSE, results='asis', warning=FALSE}
walk(names(design_groups), function(group_name) {

  cat("##", group_name, "\n\n")
  cat("::: panel-tabset\n\n")

  # ✅ 40 traps
  cat("### 40 Traps\n\n")
  for (d in design_groups[[group_name]]) {
    plot_block(AllResults40, d, se = TRUE)
  }

  # ✅ CRITICAL: TWO newlines BEFORE header
  cat("\n\n### 120 Traps\n\n")

  for (d in design_groups[[group_name]]) {
    plot_block(AllResults120, d, se = TRUE)
  }

  # ✅ closing block
  cat("\n:::\n\n")
})
```


# General comments - precision

## Grids
 - For 800 m spacing SE’s for all parameters skewed to the right (apart from S2 L0)
 - Improved for 700 m spacing, some skewness for S2 D and S2 sigma.
 - With 120 traps there are very few outliers, at 800 m spacing the most for S1 D and for 700 m spacing the most for S2 sigma

## Clusters
 - OS spacing: skewness for S2 D and sigma (as with bias)
 - 2 * sigma spacing: se’s quite tightly clustered for both strata and all parameters
 - With 120 traps there are very few outliers for both spacings

## GA4

### S1 values
 - More positive skewness in D for S2, and slightly more for S1 in sigma ses
 - With 120 traps there are very few outliers

### S2 values
 - Slight positive skewness in D for both strata, and more skew for S2 in sigma ses
 - With 120 traps some skew for S1 D is evident

### Avg values
 - Positive skewness across parameters, more so for S1
 - With 120 traps some skew for S1 D is evident with a few outliers for S1 sigma

### Both values
 - Some skew in S2 sigma but otherwise quite balanced
 - Max-min similar
 - With 120 traps tight dbns with few outliers, same for max-min

## GA5

### S1 values
 - More positive skewness in D for S2, and slightly more for S1 in sigma ses
 - With 120 traps there are very few outliers

### S2 values
 - Slight positive skew in D and sigma (mainly for S2)
 - With 120 traps very slight +ve skew in S1 D

### Avg values
 - Positive skewness in D, especially for S1
 - Slight skew in other parameters across both strata
 - Even with 120 traps substantial +ve skew in S1 D and some skew in S1 L0

### Both values
 - Very slight +ve skew in D for both, and sigma especially for S2
 - Max-min more skew for S2 D, and for sigma both are slightly skew
 - With 120 traps few outliers and mostly symmetrical dbns, with max-min a tiny bit more skewness in D and sigma for S1

## Lacework
 - Very slight skew in D and sigma for S2
 - With 120 traps few outliers and mostly symmetrical dbns