---
title: "Simulation Results (different 100 reps)"
format:
  html:
    embed-resources: true
editor: visual
---

```{r echo = FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(secr)
load("SimResults2.RData")
load("Excluded2.RData")
load("GADesigns.RData")
load("SCRObjs.RData")
load("DataSumms2.RData")
```

# Simulation setup: a 15 fold scenario

-   S1: D = 0.05 ; sigma = 200 m ; L0 = 2

-   S2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

-   reps = 100

# Grids with 800 m spacing

### Data summary

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$Grid.800, ylab = "Count", ylim = c(0,200), las = 2)
```

### Simulation Results

```{r echo = FALSE}
grids <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults$Grid.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults$Grid.D$`Rel SE`,3)),
  C4 = c(round(simresults$Grid.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults$Grid.L0$`Rel SE`,3)),
  C6 = c(round(simresults$Grid.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults$Grid.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded$Grid.S1)[1], dim(excluded$Grid.S2)[1])
)
colnames(grids) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 800 m Grids", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

# GA4 Designs (min(n,r))

## Data summaries

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.S1, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.S2, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.Avg, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.Both, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.BothMax, ylab = "Count", ylim = c(0,200), las = 2)
```
:::

## Simulation Results

```{r echo = FALSE}
GA4 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults$GA4.S1.D$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.D$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults$GA4.S1.D$`Rel SE`,3), round(simresults$GA4.S2.D$`Rel SE`,3), round(simresults$GA4.Avg.D$`Rel SE`,3),
         round(simresults$GA4.Both.D$`Rel SE`,3), round(simresults$GA4.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults$GA4.S1.L0$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.L0$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults$GA4.S1.L0$`Rel SE`,3), round(simresults$GA4.S2.L0$`Rel SE`,3), round(simresults$GA4.Avg.L0$`Rel SE`,3),
         round(simresults$GA4.Both.L0$`Rel SE`,3), round(simresults$GA4.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults$GA4.S1.Sig$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults$GA4.S1.Sig$`Rel SE`,3), round(simresults$GA4.S2.Sig$`Rel SE`,3), 
         round(simresults$GA4.Avg.Sig$`Rel SE`,3), round(simresults$GA4.Both.Sig$`Rel SE`,3),
         round(simresults$GA4.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA4.S1.S1)[1], dim(excluded$GA4.S1.S2)[1], dim(excluded$GA4.S2.S1)[1], dim(excluded$GA4.S2.S2)[1],
         dim(excluded$GA4.Avg.S1)[1], dim(excluded$GA4.Avg.S2)[1], dim(excluded$GA4.Both.S1)[1], dim(excluded$GA4.Both.S2)[1],
         dim(excluded$GA4.BothMax.S1)[1], dim(excluded$GA4.BothMax.S2)[1])
)

colnames(GA4) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA4 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA4 designs", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

Realisations from the proposed designs:

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4S1[[sample(1:100,1)]], add = TRUE)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4S2[[sample(1:100,1)]], add = TRUE)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4Avg[[sample(1:100,1)]], add = TRUE)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4Both[[sample(1:100,1)]], add = TRUE)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4BothMax[[sample(1:100,1)]], add = TRUE)
```
:::

Note warning messages:

-   S1 (2)
-   S2 (2)
-   Avg (9)
-   Both / BothMax (0)

# GA5 Designs (E(n2))

## Data summaries

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.S1, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.S2, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.Avg, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.Both, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.BothMax, ylab = "Count", ylim = c(0,200), las = 2)
```
:::

## Simulation Results

```{r echo = FALSE}
GA5 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults$GA5.S1.D$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.D$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults$GA5.S1.D$`Rel SE`,3), round(simresults$GA5.S2.D$`Rel SE`,3), round(simresults$GA5.Avg.D$`Rel SE`,3),
         round(simresults$GA5.Both.D$`Rel SE`,3), round(simresults$GA5.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults$GA5.S1.L0$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.L0$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults$GA5.S1.L0$`Rel SE`,3), round(simresults$GA5.S2.L0$`Rel SE`,3), round(simresults$GA5.Avg.L0$`Rel SE`,3),
         round(simresults$GA5.Both.L0$`Rel SE`,3), round(simresults$GA5.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults$GA5.S1.Sig$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults$GA5.S1.Sig$`Rel SE`,3), round(simresults$GA5.S2.Sig$`Rel SE`,3), 
         round(simresults$GA5.Avg.Sig$`Rel SE`,3), round(simresults$GA5.Both.Sig$`Rel SE`,3),
         round(simresults$GA5.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA5.S1.S1)[1], dim(excluded$GA5.S1.S2)[1], dim(excluded$GA5.S2.S1)[1], dim(excluded$GA5.S2.S2)[1],
         dim(excluded$GA5.Avg.S1)[1], dim(excluded$GA5.Avg.S2)[1], dim(excluded$GA5.Both.S1)[1], dim(excluded$GA5.Both.S2)[1],
         dim(excluded$GA5.BothMax.S1)[1], dim(excluded$GA5.BothMax.S2)[1])
)

colnames(GA5) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA5 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA5 designs", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

Realisations from the proposed designs:

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5S1[[sample(1:100,1)]], add = TRUE)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5S2[[sample(1:100,1)]], add = TRUE)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5Avg[[sample(1:100,1)]], add = TRUE)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5Both[[sample(1:100,1)]], add = TRUE)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5BothMax[[sample(1:100,1)]], add = TRUE)
```
:::

Original comments that largely still apply:

-   The behaviour of the GA4 algorithm seems to spread traps much further when using S1 or avg values. The other settings produce a fairly dense array with traps tending to be quite close together

-   The behaviour of the GA5 algorithm consistently produces clusters of traps, except when using average values. Using S2 values produces two large clusters, and using both with max-min tends to produce clusters that are more spread out compared to without max-min

-   Using avg values leads to high bias and relatively high variance in strata 1 for both genetic algorithms

-   Not sure why there is some positive bias for strata 2 when using the GA4 algorithm with S2 values, similarly not sure why a handful of reps gave problems for estimates for S2. The data summary shows more spatial recaps and less singletons for S2 (with slightly lower n).

  - this is the one thing that has changed, now when using S2 values with GA4 there is negligible bias for S2
