---
title: "Simulation Results (500 reps)"
format:
  html:
    embed-resources: true
server: shiny
editor: visual
---

```{r echo = FALSE, include=FALSE}
#| context: setup
library(knitr)
library(kableExtra)
library(secr)
library(shiny)
load("SimResults500.RData")
load("Excluded500.RData")
load("GADesigns.RData")
load("SCRObjs.RData")
load("DataSumms500.RData")
```

# Simulation setup: a 15 fold scenario

- S1: D = 0.05 ; sigma = 200 m ; L0 = 2

- S2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

- reps = 500

- a rep was excluded if:
  - an estimate was NA or infinite
  - the RSE for one of the parameters is > 100
  - an estimate was more than 5 fold away from the true value

# Grids with 800 m spacing

### Data summary

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$Grid.800, ylab = "Count", ylim = c(0,200), las = 2)
```

### Simulation Results

```{r echo = FALSE}
grids <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults$Grid800.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults$Grid800.D$`Rel SE`,3)),
  C4 = c(round(simresults$Grid800.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults$Grid800.L0$`Rel SE`,3)),
  C6 = c(round(simresults$Grid800.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults$Grid800.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded$Grid800.S1)[1], dim(excluded$Grid800.S2)[1])
)

colnames(grids) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 800 m Grids", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```


# Grids with 1600 m spacing

### Data summary

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$Grid.1600, ylab = "Count", ylim = c(0,200), las = 2)
```

### Simulation Results

```{r echo = FALSE}
grids2 <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults$Grid1600.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults$Grid1600.D$`Rel SE`,3)),
  C4 = c(round(simresults$Grid1600.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults$Grid1600.L0$`Rel SE`,3)),
  C6 = c(round(simresults$Grid1600.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults$Grid1600.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded$Grid1600.S1)[1], dim(excluded$Grid1600.S2)[1])
)

colnames(grids2) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids2 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 1600 m Grids", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

# GA4 Designs (min(n,r))

## Data summaries

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.S1, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.S2, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.Avg, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.Both, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G4.BothMax, ylab = "Count", ylim = c(0,200), las = 2)
```
:::

## Simulation Results

```{r echo = FALSE}
GA4 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults$GA4.S1.D$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.D$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults$GA4.S1.D$`Rel SE`,3), round(simresults$GA4.S2.D$`Rel SE`,3), round(simresults$GA4.Avg.D$`Rel SE`,3),
         round(simresults$GA4.Both.D$`Rel SE`,3), round(simresults$GA4.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults$GA4.S1.L0$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.L0$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults$GA4.S1.L0$`Rel SE`,3), round(simresults$GA4.S2.L0$`Rel SE`,3), round(simresults$GA4.Avg.L0$`Rel SE`,3),
         round(simresults$GA4.Both.L0$`Rel SE`,3), round(simresults$GA4.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults$GA4.S1.Sig$`Rel bias (mean)`*100,1), round(simresults$GA4.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults$GA4.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA4.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults$GA4.S1.Sig$`Rel SE`,3), round(simresults$GA4.S2.Sig$`Rel SE`,3), 
         round(simresults$GA4.Avg.Sig$`Rel SE`,3), round(simresults$GA4.Both.Sig$`Rel SE`,3),
         round(simresults$GA4.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA4.S1.S1)[1], dim(excluded$GA4.S1.S2)[1], dim(excluded$GA4.S2.S1)[1], dim(excluded$GA4.S2.S2)[1],
         dim(excluded$GA4.Avg.S1)[1], dim(excluded$GA4.Avg.S2)[1], dim(excluded$GA4.Both.S1)[1], dim(excluded$GA4.Both.S2)[1],
         dim(excluded$GA4.BothMax.S1)[1], dim(excluded$GA4.BothMax.S2)[1])
)

colnames(GA4) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA4 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA4 designs", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

Realisations from the proposed designs:

::: panel-tabset
### Using S1 values:

```{r}
numericInput("rep1",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot1")
```

```{r}
#| context: server

output$dataPlot1 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4S1[[input$rep1]], add = TRUE)
})
```

### Using S2 values:

```{r}
numericInput("rep2",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot2")
```

```{r}
#| context: server

output$dataPlot2 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4S2[[input$rep2]], add = TRUE)
})
```

### Using Avg values:

```{r}
numericInput("rep3",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot3")
```

```{r}
#| context: server

output$dataPlot3 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4Avg[[input$rep3]], add = TRUE)
})
```

### Using Both values:

```{r}
numericInput("rep4",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot4")
```

```{r}
#| context: server

output$dataPlot4 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4Both[[input$rep4]], add = TRUE)
})
```

### Using Both (max-min) values:

```{r}
numericInput("rep5",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot5")
```

```{r}
#| context: server

output$dataPlot5 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G4BothMax[[input$rep5]], add = TRUE)
})
```
:::

# GA5 Designs (E(n2))

## Data summaries

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.S1, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.S2, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.Avg, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.Both, ylab = "Count", ylim = c(0,200), las = 2)
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms$G5.BothMax, ylab = "Count", ylim = c(0,200), las = 2)
```
:::

## Simulation Results

```{r echo = FALSE}
GA5 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults$GA5.S1.D$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.D$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults$GA5.S1.D$`Rel SE`,3), round(simresults$GA5.S2.D$`Rel SE`,3), round(simresults$GA5.Avg.D$`Rel SE`,3),
         round(simresults$GA5.Both.D$`Rel SE`,3), round(simresults$GA5.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults$GA5.S1.L0$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.L0$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults$GA5.S1.L0$`Rel SE`,3), round(simresults$GA5.S2.L0$`Rel SE`,3), round(simresults$GA5.Avg.L0$`Rel SE`,3),
         round(simresults$GA5.Both.L0$`Rel SE`,3), round(simresults$GA5.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults$GA5.S1.Sig$`Rel bias (mean)`*100,1), round(simresults$GA5.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults$GA5.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults$GA5.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults$GA5.S1.Sig$`Rel SE`,3), round(simresults$GA5.S2.Sig$`Rel SE`,3), 
         round(simresults$GA5.Avg.Sig$`Rel SE`,3), round(simresults$GA5.Both.Sig$`Rel SE`,3),
         round(simresults$GA5.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA5.S1.S1)[1], dim(excluded$GA5.S1.S2)[1], dim(excluded$GA5.S2.S1)[1], dim(excluded$GA5.S2.S2)[1],
         dim(excluded$GA5.Avg.S1)[1], dim(excluded$GA5.Avg.S2)[1], dim(excluded$GA5.Both.S1)[1], dim(excluded$GA5.Both.S2)[1],
         dim(excluded$GA5.BothMax.S1)[1], dim(excluded$GA5.BothMax.S2)[1])
)

colnames(GA5) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA5 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA5 designs", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```

Realisations from the proposed designs:

::: panel-tabset
### Using S1 values:

```{r}
numericInput("rep6",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot6")
```

```{r}
#| context: server

output$dataPlot6 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5S1[[input$rep6]], add = TRUE)
})
```

### Using S2 values:

```{r}
numericInput("rep7",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot7")
```

```{r}
#| context: server

output$dataPlot7 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5S2[[input$rep7]], add = TRUE)
})
```

### Using Avg values:

```{r}
numericInput("rep8",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot8")
```

```{r}
#| context: server

output$dataPlot8 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5Avg[[input$rep8]], add = TRUE)
})
```

### Using Both values:

```{r}
numericInput("rep9",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot9")
```

```{r}
#| context: server

output$dataPlot9 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5Both[[input$rep9]], add = TRUE)
})
```

### Using Both (max-min) values:

```{r}
numericInput("rep10",
             "Number of rep:",
             value = sample(1:500,1),
             min = 0,
             max = 500,
             step = 10)
plotOutput("dataPlot10")
```

```{r}
#| context: server

output$dataPlot10 <- renderPlot({
plot(res.objs$`SCR Mask`)
plot(GA.designs$G5BothMax[[input$rep10]], add = TRUE)
})
```
:::

# General comments:

## Grid design

- The grids do not work particularly well
  - spacing of 800 m produces positive bias in D for both strata with a high RSE for strata 2. There was also a high proportion of reps that were excluded for strata 2 (17.2%, and 2.6% for strata 1).
  - spacing of 1600 m produces high positive bias in D for strata 1 along with a high RSE and an exlcusion rate of 4.8%
  - I do not understand how sigma is estimated so well, even with zero spatial recaptures the estimator for sigma appears unbiased?

## GA4 (min(n,r))

- The behaviour of the GA4 algorithm seems to spread traps much further when using S1 or avg values. I think this is due to the fairly high L0 values that make it easier to get high r so the algorithm spreads traps to increase n. The other settings produce a fairly dense array with traps tending to be quite close together.
- Using average values does not work well and results in high positive bias in D for strata 1 with a high RSE and an exclusion rate of 6.2%.
- The other configurations appear unbiased except for slight positive positive bias in D for strata 2 when using strata 1 values (and slightly lower bias for strata 1 when using strata 2 values).
- The best option appears to be using both sets of values with minimal differences between a 50-50 weighting and the max-min approach
- I'm not sure why when using S2 values there were a handful of reps (2.2%) that gave problems for S2. The data summary shows more spatial recaps and less singletons for S2 (with slightly lower n).


## GA5 (min En2)

-   The behaviour of the GA5 algorithm consistently produces clusters of traps, except when using average values. Using S2 values produces two large clusters, and using both with max-min tends to produce clusters that are more spread out compared to without max-min, and appear similar to when using S1 values. 

- Using avg values leads to high bias and variance with an exclusion rate of 5.6% in strata 1.

- Using S1 values leads to positive bias in D for S2 but not the other way round

- Using both sets of values works well. There is not a lot of difference from the max-min approach though that does seem to exhibit a low degree of positive bias in D especially for strata 2.

- GA5 seems marginally better than GA4 with slightly lower and better balance across the strata in RSE's in D

