---
title: "Simulation Results (500 reps)"
format:
  html:
    embed-resources: true
editor: visual
---

```{r echo = FALSE, include=FALSE}
#| context: setup
library(knitr)
library(kableExtra)
library(secr)
load("SCRObjs.RData")
load("Cluster/Sims/40Traps/GADesigns40.RData")
load("Cluster/Sims/120Traps/GADesigns120.RData")
load("SimResults40Traps500.RData")
load("Excluded40Traps500.RData")
load("DataSumms40Traps500.RData")
load("SimResults120Traps500.RData")
load("Excluded120Traps500.RData")
load("DataSumms120Traps500.RData")
```

# Simulation setup: a 15 fold scenario

- Strata 1: D = 0.05 ; sigma = 200 m ; L0 = 2

- Strata 2: D = 0.0033 ; sigma = 3000 m ; L0 = 0.133

- reps = 500

- a rep was excluded if:

  - an estimate was NA or infinite
  - the RSE for one of the parameters is \> 100
  - an estimate was more than 5 fold away from the true value

- measures of performance

  - relative bias
  - relative se (empirical sd / mean of all estimates)

- approaches include:
  - grids with 800 m spacing and optimal 2G spacing of 700 m
  - systematic clustered grid designs with OS (500 / 1200) or 2 * sigma spacing
  - GA4 and GaA5 designs using values from: S1 / S2 / Avg / Both / BothMax
  
- For both 40 traps and 120 traps

# Grids with 800 m spacing

### Data summary

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$Grid40.800, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$Grid120.800, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Simulation Results

```{r echo = FALSE}
grids1.40 <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults.40$Grid40.800.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.40$Grid40.800.D$`Rel SE`,3)),
  C4 = c(round(simresults.40$Grid40.800.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.40$Grid40.800.L0$`Rel SE`,3)),
  C6 = c(round(simresults.40$Grid40.800.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.40$Grid40.800.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.40$Grid40.800.S1)[1], dim(excluded.40$Grid40.800.S2)[1])
)

colnames(grids1.40) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids1.40 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 800 m Grids (40 traps)", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 

grids1.120 <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults.120$Grid120.800.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.120$Grid120.800.D$`Rel SE`,3)),
  C4 = c(round(simresults.120$Grid120.800.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.120$Grid120.800.L0$`Rel SE`,3)),
  C6 = c(round(simresults.120$Grid120.800.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.120$Grid120.800.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.120$Grid120.800.S1)[1], dim(excluded.120$Grid120.800.S2)[1])
)

colnames(grids1.120) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids1.120 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 800 m Grids (120 traps)", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 
```


# Grids with optimal 2G spacing (700 m)

The optimal spacing used here is from extending the optimalSpacing function to two groups and optimising the sum of n and r across the two strata.

### Data summary

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$Grid40.700, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$Grid120.700, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Simulation Results

```{r echo = FALSE}
grids2.40 <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults.40$Grid40.700.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.40$Grid40.700.D$`Rel SE`,3)),
  C4 = c(round(simresults.40$Grid40.700.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.40$Grid40.700.L0$`Rel SE`,3)),
  C6 = c(round(simresults.40$Grid40.700.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.40$Grid40.700.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.40$Grid40.700.S1)[1], dim(excluded.40$Grid40.700.S2)[1])
)

colnames(grids2.40) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids2.40 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 700 m Grids (40 traps)", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 

grids2.120 <- data.frame(
  C1 = c("S1", "S2"),
  C2 = c(round(simresults.120$Grid120.700.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.120$Grid120.700.D$`Rel SE`,3)),
  C4 = c(round(simresults.120$Grid120.700.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.120$Grid120.700.L0$`Rel SE`,3)),
  C6 = c(round(simresults.120$Grid120.700.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.120$Grid120.700.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.120$Grid120.700.S1)[1], dim(excluded.120$Grid120.700.S2)[1])
)

colnames(grids2.120) <- c("Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids2.120 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from 700 m Grids (120 traps)", align = c('l', rep('c',6))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,3,5,7), border_right = T) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 1, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE)

```

# Clustered Grid Designs

The clustered grids base within-cluster spacing on the smaller sigma and the between-cluster spacing on the larger sigma. Initially three different cluster configurations were tried and these two options were chosen:

1.  500 m / 1200 m: these spacings are based on optimal spacings for each sigma seperately
2.  400 m / 6000 m: these spacings are 2 \* sigma for each strata

## Data summaries

::: panel-tabset
### 500 m / 1200 m

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$Clust40.OS, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$Clust120.OS, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### 400 m / 6000 m

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$Clust40.2sig, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$Clust120.2sig, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

:::

### Simulation Results

```{r echo = FALSE}
grids4.40 <- data.frame(
  C1a = rep(c("OS (2 g)", "2 sigma"), each = 2), 
  C1b = rep(c("S1", "S2"),2),
  C2 = c(round(simresults.40$Clust40.OS.D$`Rel bias (mean)`*100,1), round(simresults.40$Clust40.2sig.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.40$Clust40.OS.D$`Rel SE`,3), round(simresults.40$Clust40.2sig.D$`Rel SE`,3)),
  C4 = c(round(simresults.40$Clust40.OS.L0$`Rel bias (mean)`*100,1), round(simresults.40$Clust40.2sig.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.40$Clust40.OS.L0$`Rel SE`,3), round(simresults.40$Clust40.2sig.L0$`Rel SE`,3)),
  C6 = c(round(simresults.40$Clust40.OS.Sig$`Rel bias (mean)`*100,1), round(simresults.40$Clust40.2sig.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.40$Clust40.OS.Sig$`Rel SE`,3), round(simresults.40$Clust40.2sig.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.40$Clust40.os.S1)[1], dim(excluded.40$Clust40.os.S2)[1], dim(excluded.40$Clust40.2sig.S1)[1], dim(excluded.40$Clust40.2sig.S2)[1])
)

colnames(grids4.40) <- c("Config", "Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids4.40 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from Clustered Grids (40 traps)", align = c('l', rep('c',8))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 

grids4.120 <- data.frame(
  C1a = rep(c("OS (2 g)", "2 sigma"), each = 2), 
  C1b = rep(c("S1", "S2"),2),
  C2 = c(round(simresults.120$Clust120.OS.D$`Rel bias (mean)`*100,1), round(simresults.120$Clust120.2sig.D$`Rel bias (mean)`*100,1)),
  C3 = c(round(simresults.120$Clust120.OS.D$`Rel SE`,3), round(simresults.120$Clust120.2sig.D$`Rel SE`,3)),
  C4 = c(round(simresults.120$Clust120.OS.L0$`Rel bias (mean)`*100,1), round(simresults.120$Clust120.2sig.L0$`Rel bias (mean)`*100,1)),
  C5 = c(round(simresults.120$Clust120.OS.L0$`Rel SE`,3), round(simresults.120$Clust120.2sig.L0$`Rel SE`,3)),
  C6 = c(round(simresults.120$Clust120.OS.Sig$`Rel bias (mean)`*100,1), round(simresults.120$Clust120.2sig.Sig$`Rel bias (mean)`*100,1)),
  C7 = c(round(simresults.120$Clust120.OS.Sig$`Rel SE`,3), round(simresults.120$Clust120.2sig.Sig$`Rel SE`,3)),
  C8 = c(dim(excluded.120$Clust120.os.S1)[1], dim(excluded.120$Clust120.os.S2)[1], dim(excluded.120$Clust120.2sig.S1)[1], dim(excluded.120$Clust120.2sig.S2)[1])
)

colnames(grids4.120) <- c("Config", "Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

grids4.120 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from Clustered Grids (120 traps)", align = c('l', rep('c',8))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(2,  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE)
```

# GA4 Designs (min(n,r))

## Data summaries

::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G4.40.S1, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$G4.120.S1, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G4.40.S2, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$G4.120.S2, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G4.40.Avg, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$G4.120.Avg, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G4.40.Both, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$G4.120.Both, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G4.40.BothMax, ylab = "Count", ylim = c(0,400), las = 2, main = "40 Traps")
boxplot(datasumms.120$G4.120.BothMax, ylab = "Count", ylim = c(0,400), las = 2, main = "120 Traps")
```
:::

## Simulation Results
  
```{r echo = FALSE}
GA4.40 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults.40$GA4.40.S1.D$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.Avg.D$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults.40$GA4.40.S1.D$`Rel SE`,3), round(simresults.40$GA4.40.S2.D$`Rel SE`,3), round(simresults.40$GA4.40.Avg.D$`Rel SE`,3),
         round(simresults.40$GA4.40.Both.D$`Rel SE`,3), round(simresults.40$GA4.40.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults.40$GA4.40.S1.L0$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.Avg.L0$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults.40$GA4.40.S1.L0$`Rel SE`,3), round(simresults.40$GA4.40.S2.L0$`Rel SE`,3), round(simresults.40$GA4.40.Avg.L0$`Rel SE`,3),
         round(simresults.40$GA4.40.Both.L0$`Rel SE`,3), round(simresults.40$GA4.40.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults.40$GA4.40.S1.Sig$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults.40$GA4.40.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA4.40.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults.40$GA4.40.S1.Sig$`Rel SE`,3), round(simresults.40$GA4.40.S2.Sig$`Rel SE`,3), 
         round(simresults.40$GA4.40.Avg.Sig$`Rel SE`,3), round(simresults.40$GA4.40.Both.Sig$`Rel SE`,3),
         round(simresults.40$GA4.40.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA4.40.S1.S1)[1], dim(excluded$GA4.40.S1.S2)[1], dim(excluded$GA4.40.S2.S1)[1], dim(excluded$GA4.40.S2.S2)[1],
         dim(excluded$GA4.40.Avg.S1)[1], dim(excluded$GA4.40.Avg.S2)[1], dim(excluded$GA4.40.Both.S1)[1], dim(excluded$GA4.40.Both.S2)[1],
         dim(excluded$GA4.40.BothMax.S1)[1], dim(excluded$GA4.40.BothMax.S2)[1])
)

colnames(GA4.40) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA4.40 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA4 designs (40 traps)", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 

GA4.120 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults.120$GA4.120.S1.D$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.Avg.D$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults.120$GA4.120.S1.D$`Rel SE`,3), round(simresults.120$GA4.120.S2.D$`Rel SE`,3), round(simresults.120$GA4.120.Avg.D$`Rel SE`,3),
         round(simresults.120$GA4.120.Both.D$`Rel SE`,3), round(simresults.120$GA4.120.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults.120$GA4.120.S1.L0$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.Avg.L0$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults.120$GA4.120.S1.L0$`Rel SE`,3), round(simresults.120$GA4.120.S2.L0$`Rel SE`,3), round(simresults.120$GA4.120.Avg.L0$`Rel SE`,3),
         round(simresults.120$GA4.120.Both.L0$`Rel SE`,3), round(simresults.120$GA4.120.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults.120$GA4.120.S1.Sig$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults.120$GA4.120.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA4.120.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults.120$GA4.120.S1.Sig$`Rel SE`,3), round(simresults.120$GA4.120.S2.Sig$`Rel SE`,3), 
         round(simresults.120$GA4.120.Avg.Sig$`Rel SE`,3), round(simresults.120$GA4.120.Both.Sig$`Rel SE`,3),
         round(simresults.120$GA4.120.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA4.120.S1.S1)[1], dim(excluded$GA4.120.S1.S2)[1], dim(excluded$GA4.120.S2.S1)[1], dim(excluded$GA4.120.S2.S2)[1],
         dim(excluded$GA4.120.Avg.S1)[1], dim(excluded$GA4.120.Avg.S2)[1], dim(excluded$GA4.120.Both.S1)[1], dim(excluded$GA4.120.Both.S2)[1],
         dim(excluded$GA4.120.BothMax.S1)[1], dim(excluded$GA4.120.BothMax.S2)[1])
)

colnames(GA4.120) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA4.120 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA4 designs (120 traps)", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE)

```

Realisations from the proposed designs:
  
::: panel-tabset
### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G4S1[[sample(1:500,1)]], add = TRUE,  main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G4S1[[sample(1:500,1)]], add = TRUE,  main = "120 Traps")
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G4S2[[sample(1:500,1)]], add = TRUE,  main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G4S2[[sample(1:500,1)]], add = TRUE,  main = "120 Traps")
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G4Avg[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G4Avg[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G4Both[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G4Both[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G4BothMax[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G4BothMax[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```
:::
  
# GA5 Designs (E(n2))
  
## Data summaries
  
::: panel-tabset

### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G5.40.S1, ylab = "Count", ylim = c(0,200), las = 2, main = "40 Traps")
boxplot(datasumms.120$G5.120.S1, ylab = "Count", ylim = c(0,200), las = 2, main = "120 Traps")
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G5.40.S2, ylab = "Count", ylim = c(0,200), las = 2, main = "40 Traps")
boxplot(datasumms.120$G5.120.S2, ylab = "Count", ylim = c(0,200), las = 2, main = "120 Traps")
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G5.40.Avg, ylab = "Count", ylim = c(0,200), las = 2, main = "40 Traps")
boxplot(datasumms.120$G5.120.Avg, ylab = "Count", ylim = c(0,200), las = 2, main = "120 Traps")
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G5.40.Both, ylab = "Count", ylim = c(0,200), las = 2, main = "40 Traps")
boxplot(datasumms.120$G5.120.Both, ylab = "Count", ylim = c(0,200), las = 2, main = "120 Traps")
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
boxplot(datasumms.40$G5.40.BothMax, ylab = "Count", ylim = c(0,200), las = 2, main = "40 Traps")
boxplot(datasumms.120$G5.120.BothMax, ylab = "Count", ylim = c(0,200), las = 2, main = "120 Traps")
```
:::
  
## Simulation Results
  
```{r echo = FALSE}
GA5.40 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults.40$GA5.40.S1.D$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.Avg.D$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults.40$GA5.40.S1.D$`Rel SE`,3), round(simresults.40$GA5.40.S2.D$`Rel SE`,3), round(simresults.40$GA5.40.Avg.D$`Rel SE`,3),
         round(simresults.40$GA5.40.Both.D$`Rel SE`,3), round(simresults.40$GA5.40.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults.40$GA5.40.S1.L0$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.Avg.L0$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults.40$GA5.40.S1.L0$`Rel SE`,3), round(simresults.40$GA5.40.S2.L0$`Rel SE`,3), round(simresults.40$GA5.40.Avg.L0$`Rel SE`,3),
         round(simresults.40$GA5.40.Both.L0$`Rel SE`,3), round(simresults.40$GA5.40.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults.40$GA5.40.S1.Sig$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults.40$GA5.40.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.40$GA5.40.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults.40$GA5.40.S1.Sig$`Rel SE`,3), round(simresults.40$GA5.40.S2.Sig$`Rel SE`,3), 
         round(simresults.40$GA5.40.Avg.Sig$`Rel SE`,3), round(simresults.40$GA5.40.Both.Sig$`Rel SE`,3),
         round(simresults.40$GA5.40.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA5.40.S1.S1)[1], dim(excluded$GA5.40.S1.S2)[1], dim(excluded$GA5.40.S2.S1)[1], dim(excluded$GA5.40.S2.S2)[1],
         dim(excluded$GA5.40.Avg.S1)[1], dim(excluded$GA5.40.Avg.S2)[1], dim(excluded$GA5.40.Both.S1)[1], dim(excluded$GA5.40.Both.S2)[1],
         dim(excluded$GA5.40.BothMax.S1)[1], dim(excluded$GA5.40.BothMax.S2)[1])
)

colnames(GA5.40) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA5.40 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA5 designs (40 traps)", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE) 

GA5.120 <- data.frame(
  C1 = c(rep("S1",2), rep("S2",2), rep("Avg",2), rep("Both",2), rep("Both (Max)",2)),
  C2 = c(rep(c("S1","S2"),5)),
  C3 = c(round(simresults.120$GA5.120.S1.D$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.S2.D$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.Avg.D$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.Both.D$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.BothMax.D$`Rel bias (mean)`*100,1)),
  C4 = c(round(simresults.120$GA5.120.S1.D$`Rel SE`,3), round(simresults.120$GA5.120.S2.D$`Rel SE`,3), round(simresults.120$GA5.120.Avg.D$`Rel SE`,3),
         round(simresults.120$GA5.120.Both.D$`Rel SE`,3), round(simresults.120$GA5.120.BothMax.D$`Rel SE`,3)),
  C5 = c(round(simresults.120$GA5.120.S1.L0$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.S2.L0$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.Avg.L0$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.Both.L0$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.BothMax.L0$`Rel bias (mean)`*100,1)),
  C6 = c(round(simresults.120$GA5.120.S1.L0$`Rel SE`,3), round(simresults.120$GA5.120.S2.L0$`Rel SE`,3), round(simresults.120$GA5.120.Avg.L0$`Rel SE`,3),
         round(simresults.120$GA5.120.Both.L0$`Rel SE`,3), round(simresults.120$GA5.120.BothMax.L0$`Rel SE`,3)),
  C7 = c(round(simresults.120$GA5.120.S1.Sig$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.S2.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.Avg.Sig$`Rel bias (mean)`*100,1), round(simresults.120$GA5.120.Both.Sig$`Rel bias (mean)`*100,1), 
         round(simresults.120$GA5.120.BothMax.Sig$`Rel bias (mean)`*100,1)),
  C8 = c(round(simresults.120$GA5.120.S1.Sig$`Rel SE`,3), round(simresults.120$GA5.120.S2.Sig$`Rel SE`,3), 
         round(simresults.120$GA5.120.Avg.Sig$`Rel SE`,3), round(simresults.120$GA5.120.Both.Sig$`Rel SE`,3),
         round(simresults.120$GA5.120.BothMax.L0$`Rel SE`,3)),
  C9 = c(dim(excluded$GA5.120.S1.S1)[1], dim(excluded$GA5.120.S1.S2)[1], dim(excluded$GA5.120.S2.S1)[1], dim(excluded$GA5.120.S2.S2)[1],
         dim(excluded$GA5.120.Avg.S1)[1], dim(excluded$GA5.120.Avg.S2)[1], dim(excluded$GA5.120.Both.S1)[1], dim(excluded$GA5.120.Both.S2)[1],
         dim(excluded$GA5.120.BothMax.S1)[1], dim(excluded$GA5.120.BothMax.S2)[1])
)

colnames(GA5.120) <- c("Values","Strata","RB", "RSE", "RB", "RSE","RB", "RSE", "Reps") 

GA5.120 %>%
  kbl(format = "html", booktabs = TRUE, caption = "Sim Results from GA5 designs (120 traps)", align = c(rep('l',2), rep('c',7))) %>%
  kable_styling(font_size = 24) %>%
  kable_classic_2(full_width = F) %>%
  column_spec(c(1,2,4,6,8), border_right = T) %>%
  collapse_rows(columns = 1) %>%
  row_spec(0, bold = T, extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(2,4,6,8,10),  extra_css = "border-bottom: 1px solid") %>%
  add_header_above(header = c(" " = 2, "D" = 2, "L0" = 2, "Sigma" = 2, " " = 1), border_right = TRUE, bold = TRUE)

```

Realisations from the proposed designs:
  
::: panel-tabset

### Using S1 values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G5S1[[sample(1:500,1)]], add = TRUE,  main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G5S1[[sample(1:500,1)]], add = TRUE,  main = "120 Traps")
```

### Using S2 values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G5S2[[sample(1:500,1)]], add = TRUE,  main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G5S2[[sample(1:500,1)]], add = TRUE,  main = "120 Traps")
```

### Using Avg values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G5Avg[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G5Avg[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```

### Using Both values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G5Both[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G5Both[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```

### Using Both (max-min) values:

```{r, echo = FALSE, fig.align="left"}
plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.40$G5BothMax[[sample(1:500,1)]], add = TRUE, main = "40 Traps")

plot(SCR.objs$Full$`SCR Mask`)
plot(GA.designs.120$G5BothMax[[sample(1:500,1)]], add = TRUE, main = "120 Traps")
```
:::
  
# General comments:
  
## Grid design
  
- The grids do not work particularly well
- spacing of 800 m produces positive bias in D for both strata with a high RSE for strata 2. There was also a high proportion of reps that were excluded for strata 2 (17.2%, and 2.6% for strata 1).
- spacing of 1600 m produces high positive bias in D for strata 1 along with a high RSE and an exlcusion rate of 4.8%
- I do not understand how sigma is estimated so well, even with zero spatial recaptures the estimator for sigma appears unbiased?
  
## GA4 (min(n,r))
  
- The behaviour of the GA4 algorithm seems to spread traps much further when using S1 or avg values. I think this is due to the fairly high L0 values that make it easier to get high r so the algorithm spreads traps to increase n. The other settings produce a fairly dense array with traps tending to be quite close together.
- Using average values does not work well and results in high positive bias in D for strata 1 with a high RSE and an exclusion rate of 6.2%.
- The other configurations appear unbiased except for slight positive positive bias in D for strata 2 when using strata 1 values (and slightly lower bias for strata 1 when using strata 2 values).
- The best option appears to be using both sets of values with minimal differences between a 50-50 weighting and the max-min approach
- I'm not sure why when using S2 values there were a handful of reps (2.2%) that gave problems for S2. The data summary shows more spatial recaps and less singletons for S2 (with slightly lower n).

## GA5 (min En2)

- The behaviour of the GA5 algorithm consistently produces clusters of traps, except when using average values. Using S2 values produces two large clusters, and using both with max-min tends to produce clusters that are more spread out compared to without max-min, and appear similar to when using S1 values.

- Using avg values leads to high bias and variance with an exclusion rate of 5.6% in strata 1.

- Using S1 values leads to positive bias in D for S2 but not the other way round

- Using both sets of values works well. There is not a lot of difference from the max-min approach though that does seem to exhibit a low degree of positive bias in D especially for strata 2.

- GA5 seems marginally better than GA4 with slightly lower and better balance across the strata in RSE's in D